\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2016-04-06 feedback.tex
rename results to propositions
add notes from rochester seminar to feedback

\usepackage{amssymb, amsmath, amsthm, bm}
\usepackage{graphicx,csquotes,verbatim}
\usepackage[backend=biber,block=space,style=authoryear]{biblatex}
\setlength{\bibitemsep}{\baselineskip}
\usepackage[american]{babel}
%dell laptop
\addbibresource{C:/Users/Kristy/Dropbox/Research/xBibs/tradeagreements.bib}
%\addbibresource{C:/Users/Kristy/Documents/Dropbox/Research/xBibs/tradeagreements.bib}
\renewcommand{\newunitpunct}{,}
\renewbibmacro{in:}{}

@@

\vskip.3in
Minor comments
\begin{enumerate}
	\item Page 1:  Should define gamma before using it, especially given how critical it is to the paper.
	\item Page 17: `is invariant'
	\item Page 26: `an interior'
	\item I'm wondering why are the results referred to as `Results' and not `Propositions'?  Odd question when I put it like that!  But since we're used to `Propositions', saying `Results' is a bit distracting.  Or maybe I'm just being old fashioned ;-)
\end{enumerate}

@@

>>>>

\usepackage{amssymb, amsmath, amsthm, bm}
\usepackage[normalem]{ulem}
\usepackage{graphicx,csquotes,verbatim}
\usepackage[backend=biber,block=space,style=authoryear]{biblatex}
\setlength{\bibitemsep}{\baselineskip}
\usepackage[american]{babel}
%dell laptop
\addbibresource{C:/Users/Kristy/Dropbox/Research/xBibs/tradeagreements.bib}
%\addbibresource{C:/Users/Kristy/Documents/Dropbox/Research/xBibs/tradeagreements.bib}
\renewcommand{\newunitpunct}{,}
\renewbibmacro{in:}{}

@@

\vskip.3in
Minor comments
\begin{enumerate}
	\item Page 1:  Should define gamma before using it, especially given how critical it is to the paper.
	\item \sout{Page 17: `is invariant'} DONE
	\item \sout{Page 26: `an interior'} DONE
	\item \sout{I'm wondering why are the results referred to as `Results' and not `Propositions'?  Odd question when I put it like that!  But since we're used to `Propositions', saying `Results' is a bit distracting.  Or maybe I'm just being old fashioned ;-)} DONE
\end{enumerate}

@@

\newpage
Rochester Seminar, April 6, 2016 (Mostly Mark Bils)
\begin{itemize}
	\item Need to say that I'm ruling out side payments so it's clear that there can't just be a menu of punishments that exactly keeps each government in line
		\begin{itemize}
			\item Risk (average) vs. incentives (marginal) impossibility result --- but with no money transfers, even this breaks down
			\item Can I think of this as an insurance problem between the governments?
		\end{itemize}
	\item Show what the optimum is, then why they can't get it, how they have to try to mimic it with these instruments (tariff caps, escape clause, these types of punishments, etc.)
	\item Going from $\ga(s)$ to $\ga(e)$ --- essentially taking away the structure of the $s$'s was confusing b/c the policy space doesn't make any sense
\end{itemize}
